---
title: Fannie Performance
output: html_document
date: "2024-03-09"
---
Fannie Cohort Performance 

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
# https://stackoverflow.com/questions/61771543/assigning-colors-to-table-values-using-choroplethr

library(knitr)
library(dplyr)
library(tidyverse)
library(choroplethr)
library(choroplethrMaps)
library(choroplethrZip)
library(kableExtra)


delay_code_labels <- NULL
knit_hooks$set(delay = function(before, options, envir) {
    if (before) {
        delay_code_labels <<- append(delay_code_labels, options$label)
        return(NULL)  ## otherwise knitr will print delay_code_labels every time
    } else {
        
    }
})
opts_chunk$set(delay = TRUE, echo = FALSE, message = FALSE, warning = FALSE, 
              fig.align='left', fig.width = 8,fig.height=4,dpi=300)

```

```{r }
setwd('/home/shino/00 SF Loan Performance/00nano/99perf')
shellscript<-'./run_sql_v22.sh'
sql<-'fn_v81.sql'
# speeds by loan size
#params<-'TERM=360 VINT=2019 ELIG BYAGE BYBSTP B0=085 B1=110 B2=125 B3=150 B4=175 B5=200 B6=225 B7=250 B8=275 B9=500'
#params<-'TERM=360 VINT=2019 ELIG BYAGE BYBSTP B0=150 B1=200 B2=250'
# speeds by second home
#params<-'TERM=360 VINT=2018 ELIG BYAGE BY2HOM MINCOUNT=100'
#params<-'TERM=360 VINT=2018 BYAGE BY2HOM'
#params<-'TERM=360 VINT=2019 ELIG BYAGE BY2HOM'
params<-'TERM=360 VINT=2019 BYAGE BY2HOM'
#params<-'TERM=360 VINT=2020 ORIGMO=202001,202002,202003,202004,202005,202006 ELIG BYAGE BY2HOM'
#params<-'TERM=360 VINT=2020 ORIGMO=202007,202008,202009,202010,202011,202012 ELIG BYAGE BY2HOM'
#params<-'TERM=360 VINT=2021 ORIGMO=202101,202102,202103,202104,202105,202106 ELIG BYAGE BY2HOM'
#params<-'TERM=360 VINT=2021 ORIGMO=202107,202108,202109,202110,202111,202112 ELIG BYAGE BY2HOM'

#params<-'TERM=360 VINT=2018 ELIG ST=NY BYAGE BY2HOM MINCOUNT=100'
#params<-'TERM=360 VINT=2019 ELIG ST=NY BYAGE BY2HOM'
#params<-'TERM=360 VINT=2020 ELIG ST=NY BYAGE BY2HOM MINCOUNT=100'
#params<-'TERM=360 VINT=2021 ELIG ST=NY BYAGE BY2HOM'

command<-paste(shellscript, sql, params)
prefix<-'_0-'
suffix<-'.tsv'
outfile<-paste0(prefix,gsub(' ','-',params),suffix)
overwrite<-FALSE
if(overwrite | !file.exists(outfile))
{
  system(command)
}
if(!file.exists(outfile))
{
  knitr::knit_exit()
}
cohortcf<-read.csv(outfile,sep='\t') ## ,colClasses=c("character","numeric"))
```

```{r}
factor<-"Occupancy"
FRAC<-6
maxAge<-FRAC*(trunc(max(cohortcf$Loan.Age)/FRAC)+1)
xlab<-'Loan Age (mo.)'
```

## Historical Prepayments

Parameters = `r params`.

```{r}
library(ggplot2)
title<-'Historical Prepayments'
ylab<-'1 mo. CPR'
                  #  ,color=factor(Cohort.Balance)))+
cohortcf$Cohort.2nd.Home<-as.factor(cohortcf$Cohort.2nd.Home)

ggplot(cohortcf,aes(x=Loan.Age, y=CPR
                     ,color=factor(Cohort.2nd.Home)))+
  geom_line()+
  ggtitle(paste0(title,"\n",params))+
  xlab(xlab)+
  ylab(ylab)+
  labs(color=factor)+
    scale_x_continuous(breaks=seq(0,maxAge,by=FRAC))+
            scale_y_continuous(labels=scales::percent) +
   scale_colour_brewer(palette = 'YlOrRd')

```
## Historical Delinquencies

```{r}
cohortcf$totDQ<-cohortcf$X30DD.+cohortcf$X60DD.+cohortcf$X90.DD.  # total DQ
title<-'30 Day+ Delinquency'
ylab<-'30 Day+ Delinquency'
ggplot(cohortcf,aes(x=Loan.Age, y=totDQ
                     ,color=factor(Cohort.2nd.Home)))+
  geom_line()+
  ggtitle(paste0(title,'\n',params))+
  labs(color=factor)+
  xlab(xlab)+
  ylab(ylab)+
    scale_x_continuous(breaks=seq(0,maxAge,by=FRAC))+
            scale_y_continuous(labels=scales::percent) +
   scale_colour_brewer(palette = 'YlOrRd')

```

```{r}
summary<-data.frame(matrix(nrow=nrow(cohortcf)))
colnames(summary)<-'Loan_Age'
summary$Term<-cohortcf$Cohort.Term
summary$Occ<-cohortcf$Cohort.2nd.Home
summary$MAP_Elig.<-cohortcf$Cohort.MAP.Eligible
summary$Orig._Loan_Count<-cohortcf$Cohort.Orig..
summary$Orig._UPB<-cohortcf$Cohort.Orig...1
summary$Orig._ALS<-summary$Orig._UPB/summary$Orig._Loan_Count
summary$Loan_Age<-cohortcf$Loan.Age
summary$CPR_pct<-cohortcf$CPR
summary$D30_pct<-cohortcf$X30DD.
summary$D60_pct<-cohortcf$X60DD.
summary$D90plus_pct<-cohortcf$X90.DD.
summary$Rate<-cohortcf$WA.Rate

  colnames(summary) <- sub("_pct", " %", colnames(summary))
  colnames(summary) <- sub("plus", "+", colnames(summary))
  colnames(summary) <- sub("_gt_", " > ", colnames(summary))
  colnames(summary) <- gsub("_", " ", colnames(summary))
  
  
summary %>%
      mutate(across(c('Orig. UPB','Orig. Loan Count','Orig. ALS'),     function(x)format(x,scientific=FALSE,big.mark=',',digits=1,nsmall=0))) %>% 
     mutate(across(colnames(summary)[grep(' %$',colnames(summary))], function(x)paste0(format(x*100,scientific=FALSE,digits=2,nsmall=0),'%'))) %>% 
     mutate(across(c(Rate), function(x)format(x,scientific=FALSE,digits=4,nsmall=3))) %>% 
         mutate_if(is.numeric, format, digits=3,nsmall = 0) %>%  
      kbl(align=c(rep('r',ncol(summary)))) %>%
      kable_styling(bootstrap_options = c("striped","condensed"),font_size = 11)  %>%
    row_spec(0, align='center', angle = 0) 
```

# Appendices: Source listings and Environment

## Source Listing: `r knitr::current_input()`

```{r codeprint, echo = TRUE, eval = FALSE, ref.label = delay_code_labels, delay = FALSE}
```

## Query Listing: `r sql`

`r sql` queries the Fannie CRT monthly tables for performance reporting.
```sql
`r xfun::file_string(sql)`
```
```{r echo=FALSE}
cppfile <- system(paste("fgrep include",sql,"| sed -e 's/^[^\"]*\"\\([^\"]*\\)\"/\\1/'"), intern = TRUE)
```

## Source Listing: `r cppfile`
`r cppfile` contains simple macros which assist formatting of sql output.
```sql
`r xfun::file_string(paste0("../",cppfile))`
```
## Query Listing: `r shellscript`

`r shellscript` utility script to pass parameters to and 
enable specific output and define cohort groupings to the performance script `r sql`.
```sql
`r xfun::file_string(shellscript)`
```


## Environment

This script was executed in the following R environment.
```{r}
sessionInfo()
```

