---
title: Fannie Performance
output: html_document
date: "2024-03-09"
---
Fannie Cohort Performance 

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
# https://stackoverflow.com/questions/61771543/assigning-colors-to-table-values-using-choroplethr

library(knitr)
library(choroplethr)
library(choroplethrMaps)
library(choroplethrZip)
delay_code_labels <- NULL
knit_hooks$set(delay = function(before, options, envir) {
    if (before) {
        delay_code_labels <<- append(delay_code_labels, options$label)
        return(NULL)  ## otherwise knitr will print delay_code_labels every time
    } else {
        
    }
})
opts_chunk$set(delay = TRUE, echo = FALSE, message = FALSE, warning = FALSE, 
              fig.align='left', fig.width = 8,fig.height=4,dpi=300)

```

```{r }
setwd('/home/shino/00 SF Loan Performance/00nano/99perf')
# ./run_sql_v22.sh fn_v77.sql TERM=360 VINT=2019 ELIG BYAGE B0=085 B1=110 B2=125 B3=150 B4=175 B5=200 B6=225 B7=250 B8=275 B9=500

shellscript<-'./run_sql_v22.sh'
sql<-'fn_v80.sql'
params<-'TERM=360 VINT=2019 ELIG BYAGE BYBSTP B0=085 B1=110 B2=125 B3=150 B4=175 B5=200 B6=225 B7=250 B8=275 B9=500'
params<-'TERM=360 VINT=2019 ELIG BYAGE BYBSTP B0=150 B1=200 B2=250'
params<-'TERM=360 VINT=2020 ORIGMO=202001,202002,202003 ELIG BYAGE BY2HOM'
command<-paste(shellscript, sql, params)
prefix<-'_0-'
suffix<-'.tsv'
outfile<-paste0(prefix,gsub(' ','-',params),suffix)
overwrite<-FALSE
if(overwrite | !file.exists(outfile))
{
  system(command)
}
if(!file.exists(outfile))
{
  knitr::knit_exit()
}
cohortcf<-read.csv(outfile,sep='\t') ## ,colClasses=c("character","numeric"))
```

## Historical Prepayments

Parameters = `r params`.

```{r}
library(ggplot2)
FRAC<-6
maxAge<-FRAC*(trunc(max(cohortcf$Loan.Age)/FRAC)+1)
                  #  ,color=factor(Cohort.Balance)))+
cohortcf$Cohort.2nd.Home<-as.factor(cohortcf$Cohort.2nd.Home)

ggplot(cohortcf,aes(x=Loan.Age, y=CPR
                     ,color=factor(Cohort.2nd.Home)))+
  geom_line()+
    scale_x_continuous(breaks=seq(0,maxAge,by=FRAC))+
            scale_y_continuous(labels=scales::percent) +
   scale_colour_brewer(palette = 'YlOrRd')

                      #   cohortcf[cohortcf$Cohort.Balance=='085K','Loan.Age'],
                      #         y=cohortcf[cohortcf$cohort.Balance=='085K','CPR'],
                      #         color="Red"))
```

# Appendices: Source listings and Environment

## Source Listing: `r knitr::current_input()`

```{r codeprint, echo = TRUE, eval = FALSE, ref.label = delay_code_labels, delay = FALSE}
```

## Query Listing: `r sql`

`r sql` queries the Fannie CRT monthly tables for performance and summary reporting.
```sql
`r xfun::file_string(sql)`
```
```{r echo=FALSE}
cppfile <- system(paste("fgrep include",sql,"| sed -e 's/^[^\"]*\"\\([^\"]*\\)\"/\\1/'"), intern = TRUE)
```

## Source Listing: `r cppfile`
`r cppfile` contains simple macros which assist formatting of sql output.
```sql
`r xfun::file_string(paste0("../",cppfile))`
```
## Query Listing: `r shellscript`

`r shellscript` utility script to pass parameters to and 
enable specific output and define cohort groupings to the performance script `r sql`.
```sql
`r xfun::file_string(shellscript)`
```


## Environment

This script was executed in the following R environment.
```{r}
sessionInfo()
```

